PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

**ADD SCORING FOR NEURO MEASURES**

# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@

>>>>

**ADD SCORING FOR NEURO MEASURES**
# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )
